The ChEMBL database as Linked Open Data

### 2012-07-17 article.tex
Updated the rest of the paper for the phase-out of Kasabi

To expose that ChEMBL-RDF data two approaches have been adopted. First, a SPARQL end point
hosted at Uppsala University, using the Open Source Virtuoso software. Use is free, but the
querying is capped, based on the estimated computational effort. Second, resources have
been made dereferencable using the Kasabi platform~\cite{kasabi}. The Kasabi hosting provides a SPARQL
end point which requires a user account. A user account can be acquired for free for casual usage,
or paid for uncapped  use.

>>>>

To expose that ChEMBL-RDF data two approaches have been adopted. First, a SPARQL end point
hosted at Uppsala University, using the Open Source Virtuoso software. Use is free, but the
querying is capped, based on the estimated computational effort. Second, resources have
been made dereferencable via the \url{http://linkedchemistry.info} resource. The Kasabi
platform~\cite{kasabi} was used for a period of time, until that project was discontinued.
The Uppsala SPARQL end point still uses resource IRIs based on this, and follow a similar
IRI pattern where linkedchemistry.info/chembl is replaced by data.kasabi.com/dataset/chembl-rdf.
